
\documentclass[12pt]{article}
\usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
\geometry{a4paper} % or letter or a5paper or ... etc
% \geometry{landscape} % rotated page geometry

% See the ``Article customise'' template for come common customisations
\usepackage[parfill]{parskip} 
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{fancyhdr}
\usepackage{enumitem}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\lhead{\textbf{Corporate Tax}}
\rhead{\textbf{Problem Set 4: Ordinary Distributions}}
\lfoot{\footnotesize CT$\_$PS$\_$4$\_$2021S}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

%%% BEGIN DOCUMENT
\begin{document}


	\textbf{Code and Regs}: 
		\begin{itemize}
				\item
					\S\S 1(h)(11)(D)(ii); 61(a)(7); 243(a)-(c); 246(c)(1) and (4); 246A;  301(a)-(f); 311;  312(a)-(c), (f), (k)(1) and (3), (n)(5); 316; 317(a); 1059(a), (b), (c)(1), (2) and (4), (d)(6), (e)(2)
				\item
					\S\S 1.312-3; 1.316-1 and -2(b) \\
		\end{itemize}

	

\begin{enumerate}


	\item Individual A forms C Corp by contributing \$100 for all of its common stock. During the year, C Corp has \$100 of taxable income.  It also earned \$10 of tax-exempt interest; earned \$50 of dividend income of which \$25 was excluded under \S 243(a)(1); received \$100 of life insurance proceeds exempt under \S101(j)(1); recognized \$20 of capital losses that it could not deduct under \S1211(a); and paid \$21 of corporate taxes.  What are its E\&Ps?
	
	\item Same facts as problem 1.  C Corp  borrows \$300 and distributes all of the borrowed proceeds to A.  What are the tax consequences to A?

	\item Review the rulings in Situations 3 and 4 in Rev. Rul. 74-164 and read Reg. \S1.316-2(a)-(c).  Is the ruling correct?
	
	\item Individual A owns 2 shares of C Corp, one with a basis of \$30 and the other with a basis of \$200.  C Corp has E\&Ps of \$150 and makes a distribution of \$120 per share to A.  What are the tax consequences to A?
	
	\item Explain the tax policy goal of \S246(c)(1) and (d)? 

	\item	On Feb.\ 1, B Corp purchased 100 shares (5\%) of C Corp stock for \$20 per share.  On Sept.\ 1, C Corp pays a distribution of \$8 per share.  What are the tax consequences to B Corp, assuming that all of the distribution is a dividend?
	
	\item 	Same facts as previous question, except B Corp purchased the shares for \$3 per share.  
	
	\item Explain the tax policy goal of \S1059(d)(6).
	
	\item On January 1, C Corp purchases 1,000 shares of Costco stock for \$300,000 (\$300 per share).  It finances 60\% of the purchase price (\$180,000) with debt borrowed from IBank.  The prior ex-dividend date was on Nov.\ 1.  On Mar.\ 1, Costco pays a dividend of \$5 per share.  (Assume that Mar.\ 1 is also the ex date.)  What are the tax consequences to C Corp? \S246A(d)(4) and 246A(d)(2).

	\item Read \S246A(d)(3)(A).  Is there another policy approach to allocate interest expense on a Corporation's portfolio stock? 
	
%	See Bittker and Eustice @ 8.22 for further exmples
	
	\item C Corp distributes appreciated property (AB, \$50,000; FMV, \$100,000) to its sole individual shareholder, A.  C Corp has \$1,000 of E\&Ps.  What are the tax consequences to C Corp (E\&Ps, G/L recognized) and to A? What other information would be useful?

	\item Same facts as prior problem, except the property's AB is \$100,000 and its FMV is \$50,000.
	
	\item Same facts as prior problem, except that the property's AB is \$50,000, its FMV is \$100,000, and the property is subject to a liability of \$125,000.  \S\S311(b)(2) and 336(b).

	\item Read \emph{Aspro v. CIR}, T.C. 2021 on the Teams page.  What's the dispute and the holding?
	
	\item Read \emph{TSN Liquidating Corp} on the Teams page.  What's the tax goal of a dividend strip transaction?  What are some potential roadblocks?  Statutory? Common law?
	\end{enumerate}
	
	






	\end{document}	  